---
title: "SCIENCE MAPPING"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: cosmo
---

```{r setup, echo=FALSE ,message=FALSE, warning=FALSE}
# Loading libraries
library(flexdashboard)
library(bibliometrix)
library(tidyverse)
library(tidytext)
library(countrycode)
library(readxl)
library(xlsx)
library(purrr)
library(janitor) # Converts a number to a date
library(plotly)
library(DT)
library(stringr)
library(rebus)

```




```{r Loading files,  echo=FALSE ,message=FALSE, warning=FALSE, include=FALSE}
 # Loading txt or bib files into R environment
#  D <- readFiles("http://bibliometrix.org/datasets/joi.txt")

  #Loading data
  setwd("C:/Users/Francisco/Documents/UEES/Research/Bibliometria/BibliometricR")
  
D <- readFiles("ISB01.bib","ISB02.bib")

  # Converting the loaded files into a R bibliographic dataframe
  M <- convert2df(D, dbsource="isi",format="bibtex")
  
  
  
```



```{r bibliometric query, ,  echo=FALSE ,message=FALSE, warning=FALSE, include=FALSE}

resultado<- biblioAnalysis(M, sep = ";")


```


```{r formating data,  echo=FALSE ,message=FALSE, warning=FALSE}

# Elimé PT
#M1 <- M %>%  mutate(PAPER_ID=row_number()) %>%  select(PAPER_ID,PT, AU,TI,SO,LA,DT,ID,DE, C1,CR, NR,PD,PY, PG ,WC, SC ,AB,DB, AU_UN,SR)


M1 <- M %>%  mutate(PAPER_ID=row_number()) %>%  select(PAPER_ID, AU,TI,SO,LA,DT,ID,DE, C1,CR, NR,PY,WC, SC ,AB,DB, AU_UN,SR,VL)


# University
university<-M1 %>% 
          select(PAPER_ID,TI,AU_UN) %>%
          unnest_tokens(UNIVERSITY, AU_UN, token = stringr::str_split, pattern = ";",to_lower = FALSE) 

  # nesting University data
by_university <-university %>% group_by(PAPER_ID,TI) %>% nest

# Adding id number
get_index <- function(df){
  
  df %>% mutate(ID_TABLE=row_number())
}

by_university <- by_university %>%   
                     mutate(data = map( .x = data, .f = get_index))%>%
                     unnest(data) %>% 
                     mutate(ID=paste(PAPER_ID,ID_TABLE, sep="_"))

#Author
author <- M1 %>% 
          select(PAPER_ID,TI,AU) %>%
          unnest_tokens(AUTHOR, AU, token = stringr::str_split, pattern = ";",to_lower = FALSE) 
  
# nesting Author data
by_author <-author %>% group_by(PAPER_ID,TI) %>% nest


by_author <- by_author %>%   
                     mutate(data = map(.f = get_index, .x = data))%>%
                     unnest(data) %>% 
                     mutate(
                            AUTHOR_TYPE=if_else(ID_TABLE==1,"AUTHOR","CO-AUTHOR"),
                            ID=paste(PAPER_ID,ID_TABLE, sep="_")) 
                     

# Ojo QUita PG,

#Gathering  University and Author and the other fields
#result <- by_university %>% inner_join(by_author, by="ID") %>% 
 #         select(ID, TI.x, AUTHOR,AUTHOR_TYPE, UNIVERSITY) %>% 
  #        rename(TI=TI.x) %>%  
   #       inner_join(M1 %>% select(TI, SO,LA,DT, NR,PY,PG,WC,SC,DB,CR), by="TI") %>% 
    #      unnest_tokens(REFERENCE, CR, token = stringr::str_split, pattern = ";",to_lower = FALSE)

#Gathering  University and Author and the other fields
result <- by_university %>% inner_join(by_author, by="ID") %>% 
          select(ID, TI.x, AUTHOR,AUTHOR_TYPE, UNIVERSITY) %>% 
          rename(TI=TI.x) %>%  
          inner_join(M1 %>% select(TI, SO,LA,DT, NR,PY,WC,SC,DB,CR,VL), by="TI") %>% 
          unnest_tokens(REFERENCE, CR, token = stringr::str_split, pattern = ";",to_lower = FALSE)


#oJO quita PG
#result_summary<-result %>% group_by(ID,TI,AUTHOR, AUTHOR_TYPE,UNIVERSITY, SO,LA,DT, NR,PY,PG,WC,SC,DB) %>% #summarise(REFERENCE_NUMBER=n())  %>% arrange( desc(PY), ID)

result_summary<-result %>% group_by(ID,TI,AUTHOR, AUTHOR_TYPE,UNIVERSITY, SO,LA,DT, NR,PY,WC,SC,DB,VL) %>% summarise(REFERENCE_NUMBER=n())  %>% arrange( desc(PY), ID)



#Default 20 character target width.
swr = function(string, nwrap=20) {
  paste(strwrap(string, width=nwrap), collapse="\n")
}
swr = Vectorize(swr)

```


```{r descriptive,echo=FALSE ,message=FALSE, warning=FALSE }
#Number of total sources
maximo<- result_summary %>%  ungroup()%>% summarise(max(PY)) %>% as.integer()
minimo<- result_summary %>%  ungroup()%>% summarise(min(PY))%>% as.integer()
```


DESCRIPTIVE STATISTICS{data-icon="fa-area-chart" data-navmenu=Overall }
=====================================  

Column {data-width=250}
-------------------------------------

### PERIOD OF ANALYSIS
```{r}
valueBox(paste(minimo, " - ",maximo), icon = "fa-calendar-alt",color="teal")
```

### NUMBER OF AUTHORS
```{r}
#Number of authors (first author) # Ojo este número no coincide con el original porque la universidad disminuyó
total_first_author<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="AUTHOR") %>% select(AUTHOR) %>% count(AUTHOR, sort =TRUE) %>% summarise(n()) %>% as.integer()
valueBox(total_first_author, icon = "fa-user",color="teal")
```

### NUMBER OF COUNTRIES
```{r}
#admission_MATI_name <- "MATI_OL_2014A"
#admission_number<-admission_overall %>% filter(CURSO==admission_MATI_name) %>% select(n) %>% # # as.integer()
valueBox(0, icon = "fa-globe",color="teal")
```



Column {data-width=250}
-------------------------------------

### NUMBER OF DOCUMENTS

```{r}
#Number of total sources
total_source <-result_summary %>% group_by(TI) %>% summarise(TOTAL=n()) %>% 
                                    ungroup() %>% select(TI) %>% summarise(n()) %>%  as.integer()

valueBox(total_source, icon = "fa-file-word",color="teal")

```


### NUMBER OF CO-AUTHORS

```{r}
#Number of authors (first author) # Ojo este número no coincide con el original porque la universidad disminuyó
total_co_author<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="CO-AUTHOR") %>% select(AUTHOR) %>% count(AUTHOR, sort =TRUE) %>% summarise(n()) %>% as.integer()
valueBox(total_co_author, icon = "fa-user",color="teal")
```


### NUMBER OF UNIVERSITIES


```{r}

#admission_MATI_name <- "MATI_OL_2014A"
#admission_number<-admission_overall %>% filter(CURSO==admission_MATI_name) %>% select(n) %>% # # as.integer()
valueBox(0, icon = "fa-university",color="teal")

```


Column {data-width=500}
-------------------------------------

### DOCUMENT TYPE:Graph

```{r}
total_source_type<-M1 %>% count(DT) %>%rename(AMMOUNT = n, SOURCE=DT) %>% mutate(TOTAL= total_source) %>% mutate(PERCENTAGE=round(AMMOUNT/TOTAL,2)) %>% arrange(desc(PERCENTAGE))

fig_tst<-total_source_type %>% ggplot(aes(x=reorder(SOURCE,PERCENTAGE), y=PERCENTAGE,fill=SOURCE))+
                      geom_col()+
                      geom_text(aes( label = scales::percent(PERCENTAGE)), vjust = -.00,size=3)+
                      scale_y_continuous(limits=c(0,1), labels = scales::percent)+
                      coord_flip()+
                      theme_bw()+
                      scale_fill_brewer(palette="Set3")+
                      labs(title="",x ="", y = "") 
ggplotly(fig_tst)
```


### DOCUMENT TYPE: Table

```{r}
table_tst<-total_source_type %>% select(-TOTAL) %>% mutate(PERCENTAGE=PERCENTAGE*100)
table_tst %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
```


ANNUAL PRODUCTION: Overall{data-icon="fa-calendar-check" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### ANNUAL SCIENTIFIC PRODUCTION: Overall - Graph
```{r}
anual_production_paper<-result_summary %>% ungroup() %>% select(TI,PY) %>% 
                    group_by(TI,PY) %>% summarise(count=n()) %>% 
                   ungroup() %>% count(PY) %>% rename(YEAR=PY,
                                                      AMMOUNT_PAPERS=n) %>% arrange(desc(YEAR)) 

anual_production_paper$YEAR<-as.integer(anual_production_paper$YEAR)
           
fig_ap <- anual_production_paper %>% 
                        ggplot( aes(x=YEAR,y=AMMOUNT_PAPERS))+
                        geom_line(color="blue")+
                        geom_point(aes(x=YEAR,y=AMMOUNT_PAPERS),color="red")+
                        scale_x_continuous(breaks = seq(minimo, maximo, by = 2))+
                        theme_bw()+
                        scale_fill_brewer(palette="Set3")+
                        geom_text(aes(x=YEAR,y=AMMOUNT_PAPERS,group=1,label =AMMOUNT_PAPERS),position = position_stack(vjust = .95),size=3)+
                        labs(title="",x ="Year", y = "N° papers")  
ggplotly(fig_ap)
```   

Column
-------------------------------------
### ANNUAL SCIENTIFIC PRODUCTION:Overall - Table

```{r}
anual_production_paper %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
```   
 

ANNUAL PRODUCTION: Document type{data-icon="fa-calendar-check" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### ANNUAL SCIENTIFIC PRODUCTION:Document type - Graph
```{r}
anual_production_document<-result_summary %>% ungroup() %>% select(TI,PY,DT) %>% 
                    group_by(TI,PY,DT) %>% summarise(count=n()) %>% 
                   ungroup() %>% group_by(PY,DT) %>% summarise(TOTAL=n()) %>%
                    ungroup() %>% rename(YEAR=PY,AMMOUNT_PAPERS=TOTAL,DOCUMENT_TYPE=DT) %>%  arrange(desc(YEAR)) 

anual_production_document$YEAR<-as.integer(anual_production_document$YEAR)

# Create line breaks in Year
anual_production_document$DOCUMENT_TYPE <- swr(anual_production_document$DOCUMENT_TYPE)       

    
fig_apdt <- anual_production_document %>% 
                        ggplot( aes(x=YEAR,y=AMMOUNT_PAPERS))+
                        geom_line(color="blue")+
                        geom_point(aes(x=YEAR,y=AMMOUNT_PAPERS),color="red")+
                        scale_x_continuous(breaks = seq(minimo, maximo, by = 2))+
                        theme_bw()+
                        scale_fill_brewer(palette="Set3")+
                        geom_text(aes(x=YEAR,y=AMMOUNT_PAPERS,group=1,label =AMMOUNT_PAPERS),position = position_stack(vjust = .95),size=3)+
                        facet_wrap(~DOCUMENT_TYPE)+
                        theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                        labs(title="",x ="Year", y = "N° papers") 
                 
ggplotly(fig_apdt)
```   

Column
-------------------------------------
### ANNUAL SCIENTIFIC PRODUCTION::Document type - Table

```{r}
anual_production_document %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
) 
```   
 
 
 ANNUAL PRODUCTION:Knowledege Area{data-icon="fa-calendar-check" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### ANNUAL SCIENTIFIC PRODUCTION:Knowledege Area - Graph
```{r}
anual_production_area<-result_summary %>% ungroup() %>% select(TI,PY,WC) %>% 
                    group_by(TI,PY,WC) %>% summarise(count=n()) %>% 
                   ungroup() %>% group_by(PY,WC) %>% summarise(TOTAL=n()) %>%
                    ungroup() %>% rename(YEAR=PY,AMMOUNT_PAPERS=TOTAL,KNOWLEDGE_AREA=WC) %>%  arrange(desc(YEAR)) 

anual_production_area$YEAR<-as.integer(anual_production_area$YEAR)

top_10 <- anual_production_area %>% 
          group_by(KNOWLEDGE_AREA) %>% summarise(TOTAL=sum(AMMOUNT_PAPERS)) %>% 
          ungroup() %>% arrange(desc(TOTAL)) %>% head(5) %>% select(KNOWLEDGE_AREA) %>% 
          as_vector() %>% map_chr(~.x)

anual_production_area_top <- anual_production_area %>% 
                             filter(KNOWLEDGE_AREA %in% top_10) 
# Create line breaks in Year
anual_production_area_top$KNOWLEDGE_AREA <- swr(anual_production_area_top$KNOWLEDGE_AREA)       

                            
fig_apa <- anual_production_area_top %>% 
                        ggplot( aes(x=YEAR,y=AMMOUNT_PAPERS))+
                        geom_line(color="blue")+
                        geom_point(aes(x=YEAR,y=AMMOUNT_PAPERS),color="red")+
                        scale_x_continuous(breaks = seq(minimo, maximo, by = 2))+
                        theme_bw()+
                        scale_fill_brewer(palette="Set3")+
                        geom_text(aes(x=YEAR,y=AMMOUNT_PAPERS,group=1,label =AMMOUNT_PAPERS),position = position_stack(vjust = .95),size=3)+
                        facet_wrap(~KNOWLEDGE_AREA)+
                         theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                        labs(title="",x ="Year", y = "N° papers") 
                     
ggplotly(fig_apa)
```   

Column
-------------------------------------
### ANNUAL SCIENTIFIC PRODUCTION:Knowledege Area - Table

```{r}
anual_production_area  %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 
```   
 


AUTHOR PRODUCTION{data-icon="fa-user" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### AUTHOR PRODUCTION: OVERALL - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
author_production<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="AUTHOR") %>% 
                                      select(AUTHOR) %>% group_by(AUTHOR) %>% summarise(TOTAL=n()) %>% 
                                      arrange(desc(TOTAL))

fig_autp <- author_production %>% head(10) %>% 
                          ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                          geom_col(fill="light blue")+
                          geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                          coord_flip()+
                          theme_bw()+
                          scale_fill_brewer(palette="Set3")+
                          labs(title="",x ="AUTHOR", y = "N° papers")
ggplotly( fig_autp)
```   

Column
-------------------------------------
### AUTHOR PRODUCTION: OVERALL - Table
```{r }
author_production %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   
 
 
 
  
 

AUTHOR PRODUCTION:Document type{data-icon="fa-user" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### AUTHOR PRODUCTION: Document type - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
author_production_document_type<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="AUTHOR") %>% 
                                select(AUTHOR,DT) %>% group_by(AUTHOR,DT) %>% summarise(TOTAL=n()) %>%                                 rename(DOCUMENT_TYPE=DT) %>% arrange(DOCUMENT_TYPE,desc(TOTAL))

document_type <- result_summary %>%ungroup() %>%  select(DT) %>% count(DT) %>% select(DT)


#Getting the top 5 of each category
for(i in 1:nrow(document_type)) {
  if(i==1){
           var1<-author_production_document_type %>%  filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>% head(5)
  }else
  {
    var1 <- var1 %>% bind_rows(author_production_document_type %>%          filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>%head(5))
    
  }
  
}

# Create line breaks in Document Type
var1$DOCUMENT_TYPE <- swr(var1$DOCUMENT_TYPE)       

  
fig_autp_dt<- var1 %>% ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                       geom_col(fill="light blue")+
                       geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                       coord_flip()+
                       facet_wrap(~DOCUMENT_TYPE, scales="free")+
                       theme_bw()+
                       scale_fill_brewer(palette="Set3")+
                       theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                       labs(title="",x ="AUTHOR", y = "N° papers") 
ggplotly(fig_autp_dt)
```   

Column
-------------------------------------
### AUTHOR PRODUCTION: Document type - Table
```{r }
author_production_document_type %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   
  
 

AUTHOR PRODUCTION:Knowledege Area {data-icon="fa-user" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### AUTHOR PRODUCTION: Knowledege Area  - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
author_production_area<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="AUTHOR") %>% 
                                select(AUTHOR,WC) %>% group_by(AUTHOR,WC) %>% summarise(TOTAL=n()) %>%                                 rename(KNOWLEDGE_AREA=WC) %>% arrange(KNOWLEDGE_AREA,desc(TOTAL))

author_production_area_top <- author_production_area %>% 
                             filter(KNOWLEDGE_AREA %in% top_10) 

by_author_production_area_top<-author_production_area_top%>% group_by(KNOWLEDGE_AREA) %>% nest


by_author_production_area_top <- by_author_production_area_top %>%   
                     mutate(data = map( .x = data, .f = get_index))%>%
                     unnest(data) %>% filter(ID_TABLE <=5)


# Create line breaks in Document Type
by_author_production_area_top$KNOWLEDGE_AREA <- swr(by_author_production_area_top$KNOWLEDGE_AREA)       

fig_autp_a<- by_author_production_area_top %>% 
                       ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                       geom_col(fill="light blue")+
                       geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                       coord_flip()+
                       facet_wrap(~KNOWLEDGE_AREA, scales="free")+
                       theme_bw()+
                       scale_fill_brewer(palette="Set3")+
                       theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                       labs(title="",x ="AUTHOR", y = "N° papers")

ggplotly(fig_autp_a)
```   

Column
-------------------------------------
### AUTHOR PRODUCTION: Knowledege Area  - Table
```{r }
author_production_area %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   


CO-AUTHOR PRODUCTION{data-icon="fa-users" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### CO-AUTHOR PRODUCTION: OVERALL - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
author_production<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="CO-AUTHOR") %>% 
                                      select(AUTHOR) %>% group_by(AUTHOR) %>% summarise(TOTAL=n()) %>% 
                                      arrange(desc(TOTAL))

fig_autp <- author_production %>% head(10) %>% 
                          ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                          geom_col(fill="light blue")+
                          geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                          coord_flip()+
                          theme_bw()+
                          scale_fill_brewer(palette="Set3")+
                          labs(title="",x ="CO-AUTHOR", y = "N° papers")
ggplotly( fig_autp)
```   

Column
-------------------------------------
### CO-AUTHOR PRODUCTION: OVERALL - Table
```{r }
author_production %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   



CO-AUTHOR PRODUCTION:Document type{data-icon="fa-users" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### CO-AUTHOR PRODUCTION: Document type - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
  author_production_document_type<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="CO-AUTHOR") %>% 
                                  select(AUTHOR,DT) %>% group_by(AUTHOR,DT) %>% summarise(TOTAL=n()) %>%                                 rename(DOCUMENT_TYPE=DT) %>% arrange(DOCUMENT_TYPE,desc(TOTAL))
  
  document_type <- result_summary %>%ungroup() %>%  select(DT) %>% count(DT) %>% select(DT)
  
  
  #Getting the top 5 of each category
  for(i in 1:nrow(document_type)) {
    if(i==1){
             var1<-author_production_document_type %>%  filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>% head(5)
    }else
    {
      var1 <- var1 %>% bind_rows(author_production_document_type %>%          filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>%head(5))
      
    }
    
  }
  
  
  # Create line breaks in Document Type
  var1$DOCUMENT_TYPE <- swr(var1$DOCUMENT_TYPE)     
    
  fig_autp_dt<- var1 %>% ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                         geom_col(fill="light blue")+
                         geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                         coord_flip()+
                         facet_wrap(~DOCUMENT_TYPE, scales="free")+
                         theme_bw()+
                         scale_fill_brewer(palette="Set3")+
                         theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                         labs(title="",x ="CO-AUTHOR", y = "N° papers") 
  ggplotly(fig_autp_dt)
```   


Column
-------------------------------------
### CO-AUTHOR PRODUCTION: Document type - Table
```{r }
author_production_document_type %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   


CO-AUTHOR PRODUCTION:Knowledege Area {data-icon="fa-users" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### CO-AUTHOR PRODUCTION: Knowledege Area  - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
author_production_area1<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="CO-AUTHOR") %>% 
                                select(AUTHOR,WC) %>% group_by(AUTHOR,WC) %>% summarise(TOTAL=n()) %>%                                 rename(KNOWLEDGE_AREA=WC) %>% arrange(KNOWLEDGE_AREA,desc(TOTAL))

author_production_area_top1 <- author_production_area1 %>% 
                             filter(KNOWLEDGE_AREA %in% top_10) 

by_author_production_area_top1<-author_production_area_top1%>% group_by(KNOWLEDGE_AREA) %>% nest


by_author_production_area_top1 <- by_author_production_area_top1 %>%   
                     mutate(data = map( .x = data, .f = get_index))%>%
                     unnest(data) %>% filter(ID_TABLE <=5)

# Create line breaks in Year
by_author_production_area_top1$KNOWLEDGE_AREA <- swr(by_author_production_area_top1$KNOWLEDGE_AREA)

  fig_autp_a1<- by_author_production_area_top1 %>% 
                         ggplot( aes(x=reorder(AUTHOR,TOTAL),y=TOTAL))+
                         geom_col(fill="light blue")+
                         geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                         coord_flip()+
                         facet_wrap(~KNOWLEDGE_AREA, scales="free")+
                         theme_bw()+
                         theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                         labs(title="",x ="CO_AUTHOR", y = "N° papers")
  
  fig_autp_a1
  #ggplotly(fig_autp_a1) 
```   

Column
-------------------------------------
### CO-AUTHOR PRODUCTION: Knowledege Area  - Table
```{r }
author_production_area %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   



JOURNAL PRODUCTION: Overall {data-icon="fa-book" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### JOURNAL PRODUCTION: Overall  - Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
journal_production<-result_summary %>% ungroup() %>% filter(AUTHOR_TYPE=="AUTHOR") %>% 
                                      select(SO) %>% group_by(SO) %>% summarise(TOTAL=n()) %>% 
                                      arrange(desc(TOTAL)) %>% rename(JOURNAL=SO)
fig_jp <- journal_production %>% head(10) %>% 
                          ggplot( aes(x=reorder(JOURNAL,TOTAL),y=TOTAL))+
                          geom_col(fill="light blue")+
                          geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                          coord_flip()+
                          theme_bw()+
                          scale_fill_brewer(palette="Set3")+
                          labs(title="",x ="JOURNAL", y = "N° papers")
                          
ggplotly(fig_jp)       
  
```   

Column
-------------------------------------
### JOURNAL PRODUCTION: Overall  - Table
```{r }
journal_production %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   


JOURNAL PRODUCTION: Document type {data-icon="fa-book" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### JOURNAL PRODUCTION: Document type- Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
journal_production_document_type<-result_summary %>% ungroup() %>%  group_by(TI,SO,DT) %>% summarise(vALUE=n()) %>% ungroup() %>% select(SO,DT) %>% group_by(SO,DT) %>% summarise(TOTAL=n()) %>%                             rename(DOCUMENT_TYPE=DT,JOURNAL=SO) %>% arrange(DOCUMENT_TYPE,desc(TOTAL))

document_type <- result_summary %>%ungroup() %>%  select(DT) %>% count(DT) %>% select(DT)


#Getting the top 5 of each category
for(i in 1:nrow(document_type)) {
  if(i==1){
           var1<-journal_production_document_type %>%  filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>% head(3)
  }else
  {
    var1 <- var1 %>% bind_rows(journal_production_document_type %>%          filter(DOCUMENT_TYPE==document_type[i,"DT"]) %>%head(3))
    
  }
  
}

# Create line breaks in Document Type
var1$DOCUMENT_TYPE <- swr(var1$DOCUMENT_TYPE) 
var1$JOURNAL <- swr(var1$JOURNAL ) 


fig_autp_dt<- var1 %>% ggplot( aes(x=reorder(JOURNAL,TOTAL),y=TOTAL))+
                       geom_col(fill="light blue")+
                       geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                       coord_flip()+
                       facet_wrap(~DOCUMENT_TYPE, scales="free")+
                       theme_bw()+
                       scale_fill_brewer(palette="Set3")+
                       theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                       labs(title="",x ="JOURNAL", y = "N° papers")
                            
#ggplotly(fig_autp_dt)       
  
fig_autp_dt

```   

Column
-------------------------------------
### JOURNAL PRODUCTION: Document type  - Table
```{r }
journal_production_document_type %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   


JOURNAL PRODUCTION: Knowledge area {data-icon="fa-book" data-navmenu=Overall  }
=====================================  

Column
-------------------------------------

### JOURNAL PRODUCTION: Knowledge area- Graph
```{r ,echo=FALSE ,message=FALSE, warning=FALSE }
journal_production_area<-result_summary %>% ungroup() %>%  group_by(TI,WC,SO) %>% summarise(vALUE=n()) %>% ungroup() %>% select(WC,SO) %>% group_by(WC,SO) %>% summarise(TOTAL=n()) %>%                             rename(KNOWLEDGE_AREA=WC, JOURNAL=SO) %>% arrange(KNOWLEDGE_AREA,desc(TOTAL))


journal_production_area_top <- journal_production_area %>% 
                             filter(KNOWLEDGE_AREA %in% top_10) 

by_journal_production_area_top<-journal_production_area_top%>% group_by(KNOWLEDGE_AREA) %>% nest


by_journal_production_area_top <- by_journal_production_area_top %>%   
                     mutate(data = map( .x = data, .f = get_index))%>%
                     unnest(data) %>% filter(ID_TABLE <=5)

# Create line breaks in Year
by_journal_production_area_top$KNOWLEDGE_AREA <- swr(by_journal_production_area_top$KNOWLEDGE_AREA)
by_journal_production_area_top$JOURNAL<- swr(by_journal_production_area_top$JOURNAL)


fig_autp_dt<- by_journal_production_area_top %>% ggplot( aes(x=reorder(JOURNAL,TOTAL),y=TOTAL))+
                       geom_col(fill="light blue")+
                       geom_text(aes(label=TOTAL), vjust=-0.40, size=3)+
                       coord_flip()+
                       facet_wrap(~KNOWLEDGE_AREA, scales="free")+
                       theme_bw()+
                       scale_fill_brewer(palette="Set3")+
                       theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
                       labs(title="",x ="JOURNAL", y = "N° papers")

fig_autp_dt
                            
#ggplotly(fig_autp_dt)
  
```   

Column
-------------------------------------
### JOURNAL PRODUCTION: Knowledge area - Table
```{r }
journal_production_area %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```   





Author: Quality indexes{data-icon="fa-user" data-navmenu=Performance_Indicators }
===================================== 

Row {data-width=300}
-------------------------------------

### Author: Quality indexes
```{r}
authors<-gsub(","," ",names(resultado$Authors)[1:length(resultado$Authors)])
indices <- Hindex(M, field = "author", elements=authors, sep = ";", years = 50)
indices$H %>% rename(`Times Cited`=TC, `Number of Publications`=NP) %>%  datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
```


Journal: Quality indexes{data-icon="fa-book" data-navmenu=Performance_Indicators }
===================================== 

Row {data-width=300}
-------------------------------------

### Journal: Quality indexes
```{r}
journals<-gsub(","," ",names(resultado$Sources)[1:length(resultado$Sources)])
indices <- Hindex(M, field = "source", elements=journals, sep = ";", years = 50)
indices$H %>% rename(`Times Cited`=TC, `Number of Publications`=NP) %>%  datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
```


BRADFORD´S LAW{data-icon="fa-area-chart" data-navmenu=Performance_Indicators }
===================================== 

Column {data-width=500}
-------------------------------------

### Bradford´s law: Graphic
```{r}
BR <- bradford(M)
BR$graph
```

Column {data-width=500}
-------------------------------------
### Bradford´s law: Table
```{r}
BR$table %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 
```


LOTKA´S LAW{data-icon="fa-area-chart" data-navmenu=Performance_Indicators }
===================================== 

### Lotka´s law
```{r}
L <- lotka(resultado)
Observed=L$AuthorProd[,3]
# Theoretical distribution with Beta = 2
Theoretical=10^(log10(L$C)-2*log10(L$AuthorProd[,1]))

plot(L$AuthorProd[,1],Theoretical,type="l",col="red",ylim=c(0, 1), xlab="Articles",ylab="Freq. of Authors",main="Scientific Productivity")
lines(L$AuthorProd[,1],Observed,col="blue")
legend(x="topright",c("Theoretical (B=2)","Observed"),col=c("red","blue"),lty = c(1,1,1),cex=0.6,bty="n")

```


Co-citation Reference{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Intellectual_Structure }
===================================== 

Column
-------------------------------------

### Co-citation reference Network

```{r}
# Create a co-citation network
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";",  shortlabel=FALSE)

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)

clusters<- net$cluster_res  %>% select(-btw_centrality)  %>% rename(REFERENCE=vertex,CLUSTER=cluster)

```


Column
-------------------------------------

### Co-citation Reference Table

```{r}

clusters %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```


Co-coupling Reference{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Intellectual_Structure }
===================================== 


Column
-------------------------------------


### Co-coupling Reference Network

```{r}
# Create a co-citation network
NetMatrix <- biblioNetwork(M, analysis = "coupling", network = "references", sep = ";",shortlabel=FALSE)

NetMatrix <- biblioNetwork(M, analysis = "coupling", network = "references", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, n = 30, Title = "ISB Coupling Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)

clusters<- net$cluster_res  %>% select(-btw_centrality) %>% rename(REFERENCE=vertex,CLUSTER=cluster)

```

Column
-------------------------------------

### Co-coupling Reference Table

```{r}

clusters %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```



Conceptual map{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Conceptual_Map }
===================================== 

Column { .tabset}
-------------------------------------

### Keywords Co-occurrences
```{r}
# Create keyword co-occurrences network
NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```


### Conceptual Map
```{r}
CS <- conceptualStructure(M,field="ID", method="CA", minDegree=4, k.max=8, stemming=FALSE, labelsize=10, documents=10)

```


### Thematic Map

```{r}

Map=thematicMap(M, field = "ID", n = 250, minfreq = 5,
  stemming = FALSE, size = 0.5, repel = TRUE)
plot(Map$map)


```


Author Collaboration{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Social_Structure }
===================================== 

Column 
-------------------------------------

### Author Collaboration Network
```{r}
NetMatrix <- biblioNetwork(M, analysis = "collaboration",  network = "authors", sep = ";",shortlabel=FALSE)
net=networkPlot(NetMatrix,  n = 50, Title = "Author collaboration",type = "auto", size=10,size.cex=T,edgesize = 3,labelsize=0.6)


clusters<- net$cluster_res %>%select(-btw_centrality) %>%  rename(REFERENCE=vertex,CLUSTER=cluster)



```


Column 
-------------------------------------
### Author Collaboration Table
```{r}

clusters %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```



Affiliation  Collaboration{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Social_Structure }
===================================== 

Column 
-------------------------------------

### Affiliation Collaboration Network
```{r}
NetMatrix <- biblioNetwork(M, analysis = "collaboration",  network = "universities", sep = ";")
net=networkPlot(NetMatrix,  n = 50, Title = "Affiliation collaboration",type = "auto", size=10,size.cex=T,edgesize = 3,labelsize=0.6)

clusters<- net$cluster_res %>%select(-btw_centrality) %>%  rename(REFERENCE=vertex,CLUSTER=cluster)
```


Column 
-------------------------------------
### Affiliation Collaboration Table
```{r}
clusters %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 

```


Country Collaboration{data-icon="fa-area-chart" data-navmenu=Science_Mapping_Social_Structure }
===================================== 

Column 
-------------------------------------
### Country Collaboration Network

```{r}
M2<- metaTagExtraction(M, Field = "AU_CO", sep = ";")
NetMatrix <- biblioNetwork(M2, analysis = "collaboration",  network = "countries", sep = ";")
net=networkPlot(NetMatrix,  n = dim(NetMatrix)[1], Title = "Country collaboration",type = "sphere", size=10,size.cex=T,edgesize = 1,labelsize=0.6, cluster="none")

```







