---
title: "SCIENCE MAPPING"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: cosmo
---

```{r setup, echo=FALSE ,message=FALSE, warning=FALSE}
# Loading libraries
library(flexdashboard)
library(bibliometrix)
library(tidyverse)
library(tidytext)
library(countrycode)
library(readxl)
library(xlsx)
library(purrr)
library(janitor) # Converts a number to a date
library(plotly)
library(DT)
library(stringr)
library(rebus)
```



```{r Set up,  echo=FALSE ,message=FALSE, warning=FALSE, include=FALSE}
  ######### SET UP ##############

  #Loading data
  setwd("C:/Users/Francisco/Documents/Doctorado/PhD_Proposal/ScienceMapping")
 
  # Reading the final Dataframe
  finalDataFrame<-read_excel("ISB_WebOfScience.xlsx",sheet=3)
  # Giving format to the final Dataframe
  finalDataFrame <-finalDataFrame %>%  select(-REFERENCES) %>% 
                  mutate(CLUSTER=paste("Cluster ",CLUSTER))
  
  # Data formatting
  
  finalDataFrame <-finalDataFrame %>% mutate(SOURCE=str_replace_all(SOURCE,"\\\\",""))
  finalDataFrame <-finalDataFrame %>% mutate(SOURCE= str_to_title(SOURCE, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(SOURCE_ABBREVIATED= str_to_title(SOURCE_ABBREVIATED, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(TILTE= str_to_title(TILTE, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(AUTHOR= str_to_title(AUTHOR, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(CITATION= str_to_title(CITATION, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(ABSTRACT= str_to_title(ABSTRACT, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(AUTHOR_KEYWORDS= str_to_title(AUTHOR_KEYWORDS, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(WEB_OF_SCIENCE_KEYWORDS= str_to_title(WEB_OF_SCIENCE_KEYWORDS, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(LANGUAGE= str_to_title(LANGUAGE, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(DOCUMENT_TYPE= str_to_title(DOCUMENT_TYPE, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(PUBLISHER= str_to_title(PUBLISHER, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(RESEARCH_AREAS= str_to_title(RESEARCH_AREAS, locale = "en"))
  finalDataFrame <-finalDataFrame %>% mutate(AFFILIATION= str_to_title(AFFILIATION, locale = "en"))
  
  ######### SET UP ##############
```


```{r Functions ,  echo=FALSE ,message=FALSE, warning=FALSE}

 ######### FUNCTIONS ##############
  
  #Function: Default 25 character target width.
  swr <- function(string, nwrap=25) {
        paste(strwrap(string, width=nwrap), collapse="\n")
  }
  
  # Function: get Basic Operatio such as Min, Max
  getBasicOperation <- function(field, operation) {
        
    if(str_to_upper(operation)=="MIN"){
      result <-min(field)
    }  
    if(str_to_upper(operation)=="MAX"){
      result <-max(field)
    }
    
    return(result %>% as.numeric())
    
  }
  
  # Function: print Table
  printTable <- function(df){

  df %>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  ))
    
  }
  
  
  # Function: Adds an id number to the dataframe
  get_index <- function(df){
  
    df %>% mutate(ID_TABLE=row_number())
  }
  
  # Function: Print the overall graph
  printGraphOverall <- function(df,graph_type,group,minData,maxData,title_graph,x_desc,y_desc){
  
  # Top 10 auhtors o co-authors   
  if(group==""){
    df <- df %>% head(20)  
  }    
  
  if(graph_type=="CITATION"){
    result<-df %>% ggplot(aes(x=reorder(CITATION,TOTAL),y=TOTAL))
  }  
    
  if(graph_type=="SOURCE"){
    result<-df %>% ggplot(aes(x=reorder(SOURCE,TOTAL),y=TOTAL))
  }
  
  if(graph_type=="FIRST AUTHOR"){
    result<-df %>% ggplot(aes(x=reorder(AUTHORS,TOTAL),y=TOTAL))
  }
            result<- result+ geom_col(fill="light blue")+ 
                     geom_text(aes(label=TOTAL), vjust=-0.20, size=3)+
                     coord_flip()
                   
            
  if(group=="CLUSTER"){
    result<- result+ facet_wrap(.~ CLUSTER,scales="free_y")
  }

    result<- result+theme_bw()+
                     theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2)) +
                     labs(title=title_graph,x =x_desc, y = y_desc)
            
  
  return(result)
  
  }
  
  
# Function: Print the overall graph
  printGraphYear <- function(df,graph_type,group,minData,maxData,title_graph,x_desc,y_desc){
   
  result<-df%>% ggplot(aes(x=reorder(PUBLICATION_YEAR,TOTAL),y=TOTAL))+
           geom_point(aes(x=PUBLICATION_YEAR,y=TOTAL),color="red")+
           theme_bw()
  
  if(graph_type=="PUBLICATION YEAR"){
     result<-result+  geom_line( aes(x=PUBLICATION_YEAR,y=TOTAL,color="blue"))
  }
  
    
   if(graph_type=="SOURCE"){
     result <- result +geom_text(aes(x=PUBLICATION_YEAR,y=TOTAL,group=1,label =SOURCES),position =   position_stack(vjust=.95),size=1.5,angle = 45)
  }
  
  if(graph_type=="FIRST AUTHOR"){
     result <- result +geom_text(aes(x=PUBLICATION_YEAR,y=TOTAL,group=1,label =AUTHOR),position =   position_stack(vjust=.95),size=1.5,angle = 45)
  }
  
  result <- result+
            scale_x_continuous(breaks = seq(minData,maxData, by = 2))+
            theme(axis.text.x=element_text(angle=90,hjust=0.95,vjust=0.2))+
            labs(title=title_graph,x =x_desc, y = y_desc)
  
  if(group=="CLUSTER"){
    result<- result+ facet_wrap(.~ CLUSTER,scales="free_y")
  }
  
   return(result)     
  
  }
  
  ######### FUNCTIONS ##############

```



```{r Data Wrangling ,  echo=FALSE ,message=FALSE, warning=FALSE}

 ######### DATA WRANGLING ############## 
  
  # Vectorizing the \n
  swr <- Vectorize(swr)
  
  # Creating a line break in the Source 
  finalDataFrame$SOURCE<- swr(finalDataFrame$SOURCE)
  
 
  # Geting max and min of Publication Year
  minYear<- getBasicOperation(finalDataFrame$PUBLICATION_YEAR,"MIN")
  maxYear<- getBasicOperation(finalDataFrame$PUBLICATION_YEAR,"MAX")
  
  # Author
  author <- finalDataFrame %>% 
          select(PAPER_ID,AUTHOR,SOURCE,PUBLICATION_YEAR,CLUSTER) %>%
          unnest_tokens(AUTHORS,AUTHOR,token = stringr::str_split, 
                        pattern = ";",to_lower = FALSE) 
  # nesting Author data
  by_author <-author %>% group_by(PAPER_ID) %>% nest
  
  by_author <- by_author %>%   
                     mutate(data = map(.f = get_index, .x = data))%>%
                     unnest(data) %>% 
                     mutate(
                            AUTHOR_TYPE=if_else(ID_TABLE==1,"AUTHOR","CO-AUTHOR"),
                            PAPER_SUB_ID=paste(PAPER_ID,ID_TABLE, sep="_"))
  
  
information <- finalDataFrame %>% select(CITATION, CLUSTER,TIMES_CITED,PUBLICATION_YEAR)

 
   ######### DATA WRANGLING ############## 
 
```


Raw data{data-icon="fa-area-chart" data-navmenu=Information  }
=====================================  

Column 
-------------------------------------

### MAIN TABLE: RAW DATA
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
printTable(finalDataFrame)
```



Overall{data-icon="fa-area-chart" data-navmenu=Information  }
=====================================  


Column {.tabset data-width=500}
-------------------------------------


### MOST CITED ARTICLE: OVERALL (TOP 20) 
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

mostCited<-information %>% select(CITATION,TIMES_CITED) %>% arrange(desc(TIMES_CITED)) %>% 
                           rename(TOTAL=TIMES_CITED) %>% filter(!is.na(TOTAL))  

# Geting max and min of Sources
minSource<- getBasicOperation(mostCited$TOTAL,"MIN")
maxSource<- getBasicOperation(mostCited$TOTAL,"MAX")

#Printing the graph
p<-printGraphOverall(mostCited,"CITATION","",minSource,maxSource," TOP 20 Most cited:  Overall","", "Ammount of papers")
ggplotly(p)

```


### MOST CITED ARTICLE: By CLUSTER (TOP 20)
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

mostCited<-information %>% select(CITATION,TIMES_CITED,CLUSTER) %>% arrange(CLUSTER,desc(TIMES_CITED)) %>% rename(TOTAL=TIMES_CITED) %>% filter(!is.na(TOTAL))  

# Geting max and min of Sources
minSource<- getBasicOperation(mostCited$TOTAL,"MIN")
maxSource<- getBasicOperation(mostCited$TOTAL,"MAX")

#Printing the graph
p<-printGraphOverall(mostCited,"CITATION","CLUSTER",minSource,maxSource," TOP 20 Most cited: by Cluster","", "Ammount of papers")

ggplotly(p)

```


### ARTICLES: BY TIME
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

articleByTime<-information %>% select(CITATION,PUBLICATION_YEAR) %>%
                               count(PUBLICATION_YEAR) %>% rename(TOTAL=n) %>% 
                               arrange(PUBLICATION_YEAR) 


# Geting max and min of Sources
minSource<- getBasicOperation(articleByTime$PUBLICATION_YEAR,"MIN")
maxSource<- getBasicOperation(articleByTime$PUBLICATION_YEAR,"MAX")
#Printing the graph


#Printing the graph
p<-printGraphYear(articleByTime,"PUBLICATION YEAR","",minSource,maxSource,"Articles by Year","", "Ammount of Sources")
ggplotly(p)



```


### ARTICLES: BY TIME AND CLUSTER
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

articleByTime<-information %>% select(CITATION,PUBLICATION_YEAR,CLUSTER) %>%
                               count(PUBLICATION_YEAR,CLUSTER) %>% rename(TOTAL=n) %>% 
                               arrange(PUBLICATION_YEAR) 


# Geting max and min of Sources
minSource<- getBasicOperation(articleByTime$PUBLICATION_YEAR,"MIN")
maxSource<- getBasicOperation(articleByTime$PUBLICATION_YEAR,"MAX")
#Printing the graph


#Printing the graph
p<-printGraphYear(articleByTime,"PUBLICATION YEAR","CLUSTER",minSource,maxSource,"Articles by Year and Cluster","", "Ammount of Sources")
ggplotly(p)



```



### MOST CITED ARTICLE: TABLE
```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(information %>% arrange(CLUSTER,PUBLICATION_YEAR,desc(TIMES_CITED)))

```





Overall{data-icon="fa-book" data-navmenu=SOURCE  }
=====================================  

Column 
-------------------------------------

### SOURCE OVERALL: GRAPHIC (TOP 20)

```{r ,   echo=FALSE ,message=FALSE, warning=FALSE}
# Total Sources
totalSources<-finalDataFrame %>% select(SOURCE) %>%count(SOURCE) %>% 
                   rename(TOTAL=n) %>% arrange(desc(TOTAL))
# Geting max and min of Sources
minSource<- getBasicOperation(totalSources$TOTAL,"MIN")
maxSource<- getBasicOperation(totalSources$TOTAL,"MaX")
#Printing the graph
p<-printGraphOverall(totalSources,"SOURCE","",minSource,maxSource,"Co-citation: Source Overall","", "Ammount of Sources")
p

```

Column 
-------------------------------------

### SOURCE OVERALL: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
# Total Sources
totalSources<-finalDataFrame %>% select(SOURCE) %>%count(SOURCE) %>% 
                   rename(TOTAL=n) %>% arrange(desc(TOTAL))
printTable(totalSources)

```


By Year{data-icon="fa-book" data-navmenu=SOURCE  }
=====================================  


Column {data-width=600}
-------------------------------------

### SOURCE BY YEAR: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
# Total Sources by yaer
sourceYear<-finalDataFrame %>% select(SOURCE,PUBLICATION_YEAR) %>% count(SOURCE,PUBLICATION_YEAR)%>% rename(TOTAL=n) %>% arrange(PUBLICATION_YEAR) 

# Geting max and min of Sources
minSource<- getBasicOperation(sourceYear$PUBLICATION_YEAR,"MIN")
maxSource<- getBasicOperation(sourceYear$PUBLICATION_YEAR,"MAX")
#Printing the graph

repetido<- sourceYear %>% count(PUBLICATION_YEAR,TOTAL)

sourceYear<-sourceYear %>% left_join(repetido, by = c("PUBLICATION_YEAR" = "PUBLICATION_YEAR", "TOTAL" = "TOTAL")) %>% mutate(SOURCES=if_else(n==1,SOURCE,"More than one source"))

sourceYearSum<-sourceYear %>% select(SOURCES,PUBLICATION_YEAR,TOTAL) %>% 
                         count(SOURCES,PUBLICATION_YEAR,TOTAL) %>% select(-n)

#Printing the graph
p<-printGraphYear(sourceYearSum,"SOURCE","",minSource,maxSource,"Co-citation:Source by Year","", "Ammount of Sources")
p

```



Column {data-width=400}
-------------------------------------
### SOURCE BY YEAR: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(sourceYear %>% select(SOURCE,PUBLICATION_YEAR,TOTAL))

```



By Cluster{data-icon="fa-book" data-navmenu=SOURCE  }
=====================================  


Column {data-width=700}
-------------------------------------

### SOURCE OVERALL BY CLUSTER: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
# Total Sources
totalSources<-finalDataFrame %>% select(SOURCE,CLUSTER) %>%count(SOURCE,CLUSTER) %>% 
                   rename(TOTAL=n) %>% arrange(desc(TOTAL))
# Geting max and min of Sources
minSource<- getBasicOperation(totalSources$TOTAL,"MIN")
maxSource<- getBasicOperation(totalSources$TOTAL,"MaX")
#Printing the graph
p<-printGraphOverall(totalSources,"SOURCE","CLUSTER",minSource,maxSource,"Co-citation: Source Overall by Cluster","", "Ammount of Sources")
p

```

Column {data-width=300}
-------------------------------------

### SOURCE OVERALL BY CLUSTER: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(totalSources)

```



By Year and Cluster{data-icon="fa-book" data-navmenu=SOURCE  }
=====================================  


Column {data-width=750}
-------------------------------------

### SOURCE BY YEAR AND CLUSTER: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
# Total Sources by year
sourceYear<-finalDataFrame %>% select(SOURCE,PUBLICATION_YEAR,CLUSTER) %>% count(SOURCE,PUBLICATION_YEAR,CLUSTER)%>% rename(TOTAL=n) %>% arrange(PUBLICATION_YEAR) 

# Geting max and min of Sources
minSource<- getBasicOperation(sourceYear$PUBLICATION_YEAR,"MIN")
maxSource<- getBasicOperation(sourceYear$PUBLICATION_YEAR,"MAX")
#Printing the graph

repetido<- sourceYear %>% count(PUBLICATION_YEAR,TOTAL,CLUSTER)

sourceYear<-sourceYear %>% left_join(repetido, by = c("PUBLICATION_YEAR" = "PUBLICATION_YEAR", "TOTAL" = "TOTAL","CLUSTER"="CLUSTER")) %>% mutate(SOURCES=if_else(n==1,SOURCE,"More than one source"))

sourceYearSum<-sourceYear %>% select(SOURCES,PUBLICATION_YEAR,CLUSTER,TOTAL) %>% 
                         count(SOURCES,PUBLICATION_YEAR,CLUSTER,TOTAL) %>% select(-n)

#Printing the graph
p<-printGraphYear(sourceYearSum,"SOURCE","CLUSTER",minSource,maxSource,"Co-citation:Source by Year and Cluster","", "Ammount of Sources")
p
  


```


Column {data-width=250}
-------------------------------------
### SOURCE BY YEAR AND CLUSTER: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(sourceYear %>% select(SOURCE,PUBLICATION_YEAR,CLUSTER,TOTAL))

```



Overall{data-icon="fa-user" data-navmenu=FIRST_AUTHOR  }
=====================================  

Column 
-------------------------------------

### FIRST AUTHOR OVERALL: GRAPHIC (TOP 20)

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
# Total FirstAuthor
totalFirstAuthor<-by_author %>% select(AUTHORS,AUTHOR_TYPE) %>%
                                filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                count(AUTHORS) %>% 
                                rename(TOTAL=n) %>% arrange(desc(TOTAL))
# Geting max and min of First Author
minFirstAuthor<- getBasicOperation(totalFirstAuthor$TOTAL,"MIN")
maxFirstAuthor<- getBasicOperation(totalFirstAuthor$TOTAL,"MAX")
#Printing the graph
p<-printGraphOverall(totalFirstAuthor,"FIRST AUTHOR","",minFirstAuthor,maxFirstAuthor,"Co-citation: First Author Overall","", "Ammount of Sources")
p

```


Column 
-------------------------------------

### FIRST AUTHOR OVERALL: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

 # Total FirstAuthor
  totalFirstAuthor<- by_author %>% select(AUTHORS,AUTHOR_TYPE) %>%
                                  filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                  count(AUTHORS) %>% 
                                  rename(TOTAL=n) %>% arrange(desc(TOTAL))
 printTable( totalFirstAuthor)

```


By Year{data-icon="fa-user" data-navmenu=FIRST_AUTHOR   }
=====================================  


Column {data-width=700}
-------------------------------------

### FIRST AUTHOR  BY YEAR: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

totalFirstAuthorYear<- by_author %>% select(AUTHORS,AUTHOR_TYPE,PUBLICATION_YEAR) %>%
                                  filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                  count(AUTHORS,PUBLICATION_YEAR) %>% 
                                  rename(TOTAL=n) %>% arrange(desc(TOTAL))
# Geting max and min of First Author
minFirstAuthorYear<- getBasicOperation(totalFirstAuthorYear$PUBLICATION_YEAR,"MIN")
maxFirstAuthorYear<- getBasicOperation(totalFirstAuthorYear$PUBLICATION_YEAR,"MAX")

repetido<-totalFirstAuthorYear %>% count(PUBLICATION_YEAR,TOTAL)

totalFirstAuthorYear<-totalFirstAuthorYear %>% left_join(repetido, by = c("PUBLICATION_YEAR" = "PUBLICATION_YEAR", "TOTAL" = "TOTAL")) %>% mutate(AUTHOR=if_else(n==1,AUTHORS,"More than one author"))

totalFirstAuthorYearSum<-totalFirstAuthorYear %>% select(AUTHOR,PUBLICATION_YEAR,TOTAL) %>% 
                         count(AUTHOR,PUBLICATION_YEAR,TOTAL) %>% select(-n)

#Printing the graph
p<-printGraphYear(totalFirstAuthorYearSum,"FIRST AUTHOR","",minFirstAuthorYear,maxFirstAuthorYear,"Co-citation: First Author by Year","", "Ammount of Sources")
p

```



Column {data-width=300}
-------------------------------------
### FIRST AUTHOR BY YEAR: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(totalFirstAuthorYear %>% select(AUTHORS,PUBLICATION_YEAR,TOTAL))

```



By Cluster{data-icon="fa-user" data-navmenu=FIRST_AUTHOR }
=====================================  


Column {data-width=700}
-------------------------------------

### FIRST AUTHOR BY CLUSTER: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
totalFirstAuthor<-by_author %>% select(AUTHORS,AUTHOR_TYPE,CLUSTER) %>%
                                filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                count(AUTHORS,CLUSTER) %>% 
                                rename(TOTAL=n) %>% arrange(desc(TOTAL))

# Geting max and min of Sources
minSource<- getBasicOperation(totalSources$TOTAL,"MIN")
maxSource<- getBasicOperation(totalSources$TOTAL,"MAX")
#Printing the graph
p<-printGraphOverall(totalFirstAuthor,
                     "FIRST AUTHOR","CLUSTER",minFirstAuthor,maxFirstAuthor,"Co-citation: First Author by Cluster","", "Ammount of Sources")
p

```

Column {data-width=300}
-------------------------------------
### FIRST AUTHOR BY CLUSTER: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}
 totalFirstAuthor<-by_author %>% select(AUTHORS,AUTHOR_TYPE,CLUSTER) %>%
                                filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                count(AUTHORS,CLUSTER) %>% 
                                rename(TOTAL=n) %>% arrange(desc(TOTAL))
 printTable( totalFirstAuthor)

```



By Year and Cluster{data-icon="fa-user" data-navmenu=FIRST_AUTHOR }
=====================================  


Column {data-width=750}
-------------------------------------

### FIRST BY YEAR AND CLUSTER: GRAPHIC

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

totalFirstAuthorYear<- by_author %>% select(AUTHORS,AUTHOR_TYPE,PUBLICATION_YEAR,CLUSTER) %>%
                                  filter(AUTHOR_TYPE=="AUTHOR")  %>% 
                                  count(AUTHORS,PUBLICATION_YEAR,CLUSTER) %>% 
                                  rename(TOTAL=n) %>% arrange(desc(TOTAL))
# Geting max and min of First Author
minFirstAuthorYear<- getBasicOperation(totalFirstAuthorYear$PUBLICATION_YEAR,"MIN")
maxFirstAuthorYear<- getBasicOperation(totalFirstAuthorYear$PUBLICATION_YEAR,"MAX")

repetido<-totalFirstAuthorYear %>% count(PUBLICATION_YEAR,TOTAL,CLUSTER)

totalFirstAuthorYear<-totalFirstAuthorYear %>% left_join(repetido, by = c("PUBLICATION_YEAR" = "PUBLICATION_YEAR", "TOTAL" = "TOTAL", "CLUSTER"="CLUSTER")) %>% mutate(AUTHOR=if_else(n==1,AUTHORS,"More than one author"))

totalFirstAuthorYearSum<-totalFirstAuthorYear %>% select(AUTHOR,PUBLICATION_YEAR,TOTAL,CLUSTER) %>% 
                         count(AUTHOR,PUBLICATION_YEAR,TOTAL,CLUSTER) %>% select(-n)

#Printing the graph
p<-printGraphYear(totalFirstAuthorYearSum,
                  "FIRST AUTHOR","CLUSTER",minFirstAuthorYear,maxFirstAuthorYear,"Co-citation: First Author by Year and Cluster","", "Ammount of Sources")
p


```


Column {data-width=250}
-------------------------------------
### SOURCE BY YEAR AND CLUSTER: TABLE

```{r ,  echo=FALSE ,message=FALSE, warning=FALSE}

printTable(totalFirstAuthorYear %>% select(AUTHORS,PUBLICATION_YEAR,CLUSTER,TOTAL))

```

