---
title: "SCIENCE MAPPING"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: cosmo
  params:
    analysis_type: co-citation
    network_type: references
  
---

```{r setup, echo=FALSE ,message=FALSE, warning=FALSE}
# Loading libraries
library(flexdashboard)
library(bibliometrix)
library(tidyverse)
library(tidytext)
library(countrycode)
library(readxl)
library(xlsx)
library(purrr)
library(janitor) # Converts a number to a date
library(plotly)
library(DT)
library(stringr)
library(rebus)

```




```{r Loading files,  echo=FALSE ,message=FALSE, warning=FALSE, include=FALSE}
#Loading data
setwd("C:/Users/Francisco/Documents/UEES/Research/Bibliometria/BibliometricR")
  
D <- readFiles("ISB01.bib","ISB02.bib")

# Converting the loaded files into a R bibliographic dataframe
M <- convert2df(D, dbsource="isi",format="bibtex")
  
```


```{r bibliometric query, ,  echo=FALSE ,message=FALSE, warning=FALSE, include=FALSE}


resultado<- biblioAnalysis(M, sep = ";")

# Objeto de la Intellectual Structure
intellectualStructure <- function(analysis_type, network_type,separator,number ){

NetMatrix <- biblioNetwork(M, analysis = analysis_type, network = network_type, sep =separator,  shortlabel=FALSE)

# Plot the network
net=networkPlot(NetMatrix, n = number, Title = "Co-Citation Network", type = "fruchterman", size=T, remove.multiple=FALSE, labelsize=0.7,edgesize = 5)

return(net)
}

# Listado de la Intellectual Structure
listaIntellectualStructure <- function(net,number ){

lista<- net$cluster_res  %>% select(-btw_centrality)%>% rename(REFERENCE=vertex,CLUSTER=cluster) %>% 
mutate(CLUSTER_NUMBER=number)  

return(lista)
}

printTable <- function(lista ){

  listaTable<-lista%>% datatable(
   extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )) 
  
return(listaTable)
}

getEquation <- function(lista ){

  equation<-lista %>% select(REFERENCE) %>% 
            mutate(ID=row_number()) %>% 
            select(ID, REFERENCE) %>%
            mutate(REFERENCE=str_trim(REFERENCE, side = "both")) %>% 
            mutate(REFERENCE= str_replace(REFERENCE,pattern = SPC,replacement = "-")) %>% 
            mutate(REFERENCE= str_replace(REFERENCE,pattern = SPC,replacement = "_")) %>%
            mutate(REFERENCE= str_replace(REFERENCE,pattern = SPC,replacement = "_")) %>%
            mutate(REFERENCE= str_replace(REFERENCE,pattern = SPC,replacement = "-")) %>%
            separate(REFERENCE,c("AUTHOR","YEAR","JOURNAL"),sep = "_") %>% 
            mutate(AUTHOR =str_replace(AUTHOR,pattern = "-", replacement = " ")) %>% 
            mutate(JOURNAL =str_replace(JOURNAL,pattern = "-", replacement = " ")) %>% 
            mutate(EQUATION=paste( "( AU=",AUTHOR, " AND PY=",YEAR , " AND SO=",JOURNAL  ,")"  ) ) %>% select(EQUATION) 

n<- nrow(equation)
result1<-equation[1,]

for (i in 2:n){
     result1<- paste(result1," OR ",equation[i,] )
  }
  
return(result1)
  
}

```




Reference 20{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 20 Nodes

```{r}
net20 <- intellectualStructure("co-citation", "references",";",20 )
lista20 <- listaIntellectualStructure(net20,20)

```


Column
-------------------------------------

### Co-citation Reference Table: 20 Nodes

```{r}
printTable(lista20) 

```


Reference 25{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 25 Nodes

```{r}
net25 <- intellectualStructure("co-citation", "references",";",25 )
lista25 <- listaIntellectualStructure(net25,25)

```


Column
-------------------------------------

### Co-citation Reference Table: 25 Nodes

```{r}
printTable(lista25) 

```


Reference 30{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 30 Nodes

```{r}
net30 <- intellectualStructure("co-citation", "references",";",30 )
lista30 <- listaIntellectualStructure(net30,30)

```


Column
-------------------------------------

### Co-citation Reference Table: 30 Nodes

```{r}
printTable(lista30)

```



Reference 35{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 35 Nodes

```{r}
net35 <- intellectualStructure("co-citation", "references",";",35 )
lista35 <- listaIntellectualStructure(net35,35)

```


Column
-------------------------------------

### Co-citation Reference Table: 35 Nodes

```{r}
printTable(lista35)

```



Reference 40{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 40 Nodes
```{r}

net40 <- intellectualStructure("co-citation", "references",";",40 )
lista40 <- listaIntellectualStructure(net40,40)

```


Column
-------------------------------------

### Co-citation Reference Table: 40 Nodes

```{r}
printTable(lista40)

```



Reference 45{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 45 Nodes
```{r}

net45 <- intellectualStructure("co-citation", "references",";",45 )
lista45 <- listaIntellectualStructure(net45,45)

```


Column
-------------------------------------

### Co-citation Reference Table: 45 Nodes

```{r}
printTable(lista45)

```



Reference 50{data-icon="fa-area-chart" data-navmenu=Co-citation }
===================================== 

Column
-------------------------------------

### Co-citation reference Network: 50 Nodes
```{r}

net50 <- intellectualStructure("co-citation", "references",";",50 )
lista50 <- listaIntellectualStructure(net50,50)

```


Column
-------------------------------------

### Co-citation Reference Table: 50 Nodes

```{r}
printTable(lista50)

```


Overall{data-icon="fa-area-chart" data-navmenu=Data }
===================================== 

Column
-------------------------------------

### Overall table

```{r}

  lista<-bind_rows(lista20,lista25,lista30,lista40,lista45,lista50) 
  printTable(lista)
 

```


Important Information{data-icon="fa-area-chart" data-navmenu=Data }
===================================== 

Column {.tabset data-width=500}
-------------------------------------

### Influential papers
```{r}

  lista<-bind_rows(lista20,lista25,lista30,lista40,lista45,lista50) 
  printTable(lista %>% count(REFERENCE) %>% arrange(desc(n)))

```

### Cluster Number
```{r}

  lista<-bind_rows(lista20,lista25,lista30,lista40,lista45,lista50) 
  printTable(lista %>% count(CLUSTER,CLUSTER_NUMBER) %>% arrange(CLUSTER_NUMBER) %>% filter(n>=5))
 

```



Cluster 35{data-icon="fa-area-chart" data-navmenu=Data }
===================================== 



Column {.tabset data-width=500}
-------------------------------------

### 35 vs 30 No match
```{r}
 printTable( anti_join(lista35,lista30, by = "REFERENCE"))
 
```

### 35 vs 25 No match
```{r}
 printTable( anti_join(lista35,lista25, by = "REFERENCE"))
 
```


### 35 vs 20 No match
```{r}
 printTable( anti_join(lista35,lista20, by = "REFERENCE"))
 
```



WebOfScience Equation{data-icon="fa-area-chart" data-navmenu=Data }
===================================== 

Column {.tabset data-width=500}
-------------------------------------

### 20 Elements
```{r}
printTable(getEquation(lista20) %>% as.data.frame())

```

### 25 Elements
```{r}
printTable(getEquation(lista25) %>% as.data.frame())

```


### 30 Elements
```{r}
printTable(getEquation(lista30) %>% as.data.frame())
```

### 35 Elements
```{r}
printTable(getEquation(lista35) %>% as.data.frame())

```


### 40 Elements
```{r}
printTable(getEquation(lista40) %>% as.data.frame())

```


### 45 Elements
```{r}
printTable(getEquation(lista45) %>% as.data.frame())

```


### 50 Elements
```{r}
printTable(getEquation(lista50) %>% as.data.frame())

```
